---
title: "Sensitivity and Specificity"
author: "Emmeline Tsen"
date: "October 5, 2015"
output: html_document
---


## Readings

***APM***

- ***Chapter 5 Measuring Performance in Regression Models*** (esp. ***5.2 The Variance Bias Trade-Off***)  (5 pages)
- ***Chapter 11 Measuring Performance in Classification Models*** (~20 pages)
- ***Chapter 7.4 K-Nearest Neighbors (regression)*** (2 pages)
- ***Chapter 13.5 K-Nearest Neighbors (classification)*** (3 pages)


```{r, echo=FALSE, results='hide', warning=FALSE }
packs <-  c('ggplot2', 'magrittr', 'dplyr', 'caret', 'AppliedPredictiveModeling')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

.. = NULL  # For Aesthetics

```


## EXERCISE 1: Resampling

`x` is a random variable. We want to not only know what the `mean(x)` is but want to calculate the uncertainty of `mean(x)`.  Measuring the uncertainty requires repeated measurements of `mean(x)`.

- Calculate the mean of `x`.
- Calculte the `sd( mean(x) )` using the **using 10-fold cross-validation**.  Create your own folds, show your work. (An example is for the Bootstrap is given as a hint. )


```{r}
set.seed(1) 
x <- runif(20,1,20)

x_mean = mean(x)

k=10 #number of folds

# CROSS-VALIDATION
id <- sample(x, replace = FALSE) # random draws without replacement

log_models <- new.env(hash=T, parent=emptyenv()) 
for (i in 1:k){
  train <- x[id != i]
  test <- x[id == i ]
  # run algorithm, e.g. logistic regression
  #log_models[[as.character(i)]] <- lm( train ~ 1 , family="binomial", data=train)
}

sd_cv <- sd(mean(x))

# BOOTSTRAP (EXAMPLE)
sd_boot <- sapply(1:k, function(i) sample(x,replace=TRUE) %>% mean ) %>% sd

```


- sd_cv   is: `r sd_cv`
- sd_boot is: `r sd_boot`



# Exercise 2: Binomial Metrics

Here's a really simple Model of Versicolor iris based on the **iris** data :

```{r}
set.seed(1)
data(iris)

qplot( data=iris, x=Petal.Length, y=Sepal.Length, color=Species )

# Create Dependent Variable
iris$Versicolor <- 
  ifelse( iris$Species == 'versicolor', "versicolor", "other" ) %>% as.factor
iris$Species = NULL 

wh <- sample.int( nrow(iris), size=nrow(iris)/2 )
train <- iris[ wh,]
test <- iris[ -wh, ]


fit.glm <- glm( Versicolor ~ . - Sepal.Length, data=train, family=binomial )
```


Use the models to and write functions to calculate:

* Prevalence 
* Accuracy
* Error Rate / Misclassification Rate
* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision

The functions should take two logical vectors of the same length, `y` and `yhat`

```{r}

# The FPR is THE NUMBER OF FALSE POSITIVES / NEGATIVES (TN+FP)

threshold = 0.5 
y = test$Versicolor == 'versicolor'
yhat = predict(fit.glm, test, type="response") > threshold


fpr = function(y,yhat)
  sum(y & (y != yhat) ) / # FP
  sum(! y)                # N

fpr(y,yhat)

# The TPR is THE NUMBER OF TRUE POSITIVES / POSITIVES (TP + FN)

tpr = function(y,yhat){
  sum (y != yhat) / # TP
  sum(y) # P
}

tpr(y,yhat)

# The TNR is THE NUMBER OF TRUE NEGATIVES / NEGATIVES (TN + FP)
  
tnr = function(y, yhat)
  sum (y == yhat) / #TN
  sum (!y)

tnr(y,yhat)

# The PPV is THE NUMBER OF TRUE POSITIVES / PREDICTED POSITIVES
ppv = function(y,yhat)
  sum (y != yhat) /
  sum(y)

ppv(y,yhat)

prevalence = function(y,yhat) {}
accuracy   =   
error_rate = 
tpr = tpr(y,yhat)
fpr = fpr(y,yhat)
tnr = tnr(y,yhat)
sensitivity = tpr
specificity = tnr
recall = tpr 
precision = ppv(y,yhat)

```

- What is wrong with the modeling approach used?
PPV depends on the prevalence upon predictive values.




